% LaTeX resume using res.cls
\documentclass[line,margin,10pt]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\oddsidemargin -0.25in
\textwidth 5.75in

\begin{document}


\name{Abbie M. Popa, ScB \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad UC Davis Neuroscience Graduate Group}
% \address used twice to have two lines of address
%\address{1333 Arlington Blvd Apt 6, Davis, CA 95616}
%\address{phone:(401) 440 5228\\ e-mail:abbiepopa@gmail.com}


 
\begin{resume}
 
\section{AWARDS AND CERTIFICATES}
Accepted to UC Davis FUTURE Certificate Track \hfill 2015-16 Academic Year\\
UC Davis Graduate Student Asssembly Travel Award \hfill 2014-15 Academic Year\\
ERP Boot Camp (Dr. Steven J. Luck) \hfill Completed July 2014\\
UC Davis Graduate Student Asssembly Travel Award \hfill 2013-14 Academic Year

\section{PUBLICATIONS}
%\begin{itemize} \itemsep -2pt
%\item 
{\sl Submitted}: \textbf{Popa AM}, Cruz J, Wong L, Harvey D, Angkustsiri K, Leckliter I, Perez-Edgar K, Simon TJ. Seeing Eye to Eye with Threat: Atypical Threat Bias Responses in Children with 22q11.2 Deletion Syndrome.

\section{PRESENTATIONS AND POSTERS} 
\begin{itemize} \itemsep -2pt
\item \textbf{Popa AM}, Shapiro H, Harvey D, Amato M, Cruz J, Cung N, Reyes D, Simon TJ. Children with 22q11.2 Deletion Syndrome Show Lower Spatial and Temporal Acuity Than TD Children In Continuously Varying Tasks. Abstract Accepted at the 10th Biennial International 22q11.2 Conference 2016, Sirmione, Italy.
\item \textbf{Popa AM}, Hunsaker N, Deng M, Garner J, Cruz J, Cung N, Reyes D, Simon TJ. Cortical Tissue Volumes Correlate to Cavum Septum Pellucidum Size in Children with 22q11.2 Deletion Syndrome and Typical Controls. Oral Accepted at the 71st Annual Meeting of the Society of Biological Psychiatry 2016, Atlanta, GA.
\item \textbf{Popa AM}, Beaton E, Cruz J, Wong L, Cung N, Harvey D, Simon TJ. Adaptation to a Mild Stressor in Initially Anxious Children was related to their Attention to Perceived Threat in a Dot Probe Experiment. Poster Presented at the 70th Annual Meeting of the Society of Biological Psychiatry 2015, Toronto, ON, Canada.
\item \textbf{Popa AM}, Angkustsiri K, Brahmbhatt K, Cruz J, Cung N, Harvey D, Leckliter I, Reyes D, Shapiro H, Wong L, Simon TJ. Impact of Cognitive-Affective Interactions on Attentional Control, Inhibition, and Temporal Attention. Oral Presentation Accepted at the 21st International Scientific Meeting of the Velo-Cardio-Facial Syndrome Educational Foundation, Inc 2014, Las Vegas Nevada.
\item \textbf{Popa AM}, Angkustsiri K, Brahmbhatt K, Cruz J, Cung N, Leckliter I, Quintero A, Reyes D, Shapiro H, Simon TJ. Timecourse of Response to Threat Stimuli in Children with 22q11.2 Deletion Syndrome Informs Understanding of Anxiety. Oral Presented at the 9th Annual Meeting of the International 22q11.2 Foundation 2014, Mallorca, Spain.
\item Angkustsiri K, \textbf{Popa AM}, Simon TJ. Atypical Pupillary Responses To Emotional Faces in Children With Chromosome 22q11.2 Deletion Syndrome. Oral Presentaion Accepted at the Pediatric Academic Societies and Asian Society for Pediatric Research Joint Meeting 2014 Vancouver, BC, Canada.
\item \textbf{Popa AM}, Angkustsiri K, Brahmbhatt K, Cruz J, Cung N, Leckliter I, Quintero A, Reyes D, Shapiro H, Simon TJ. Atypical Adaptation  Responses to Threat Stimuli in Children with Chromosome 22q11.2 Deletion Syndrome. Poster Presented at the 69th Annual Meeting of the Society of Biological Psychiatry 2014, New York, NY.
\item Cruz JR, \textbf{Popa AM}, Wong LM, Angkustsiri K, Shapiro H, Fox N, Pine D, Perez-Edgar K, Simon TJ. Examining Attention Bias Towards Threat to Understand Cognition and Anxiety Interactions in 22q11.2DS. Poster at the 20th International Scientific Meeting of the Velo-Cardio-Facial Syndrome Educational Foundation 2013, Dublin, Ireland.
\item Cruz JR, Wong LM, Angkustsiri K, \textbf{Popa AM}, Shapiro HM, Fox N, Pine D, Perez-Edgar K, Simon TJ. Children with Chromosome 22q11.2 Deletion Syndrome Exhibit High Levels of Anxiety and Threat Bias in a Dot Probe Experiment. Poster presented at the 68th Annual Meeting of the Society of Biological Psychiatry 2013, San Francisco, CA.
\item Sullivan, M. C., Miller, R. J., Winchester, S. B., Barcelos, M., Oliveira, E., \& \textbf{Popa, A}. (2012, May). Developmental Origins Theory and HPA axis function: Evidence from a Longitudinal Study of Preterm Infants at Young Adulthood.  Poster presented at the Massachusetts General Hospital, Yvonne L. Munn Center for Nursing Research, Nursing Research Expo, Boston, MA.
\end{itemize}

%\section{SENIOR HONORS THESIS}


\end{resume}

\end{document}







