% LaTeX resume using res.cls
\documentclass[line,margin,10pt]{res} 
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 

\oddsidemargin -0.25in
\textwidth 5.75in

\begin{document}


\name{Abbie M. Popa, ScB \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad \quad UC Davis Neuroscience Graduate Group}
% \address used twice to have two lines of address
% \address{1333 Arlington Blvd Apt 6, Davis, CA 95616}
\address{(401) 440 5228}
\address {abbiepopa@gmail.com}


 
\begin{resume}
 
\section{EDUCATION} 
\textbf{PhD University of California at Davis}, Davis, CA, (September 2012 - December 2017)\\
Major: Cognitive Neuroscience\\
Advanced to Candidacy September 2015\\
\emph{Thesis Topic}: Anxiety Impacts Attentional and Inhibitory Control in Adolescence\\
\textbf{Honors ScB.}, Brown University, Providence, RI, (September 2006-December 2010)\\
                % \sl will be bold italic in New Century Schoolbook (or
	        % any postscript font) and just slanted in
		% Computer Modern (default) font
                Major: Cognitive Neuroscience\\
									\emph{Thesis Title}: Concordance of Movement and Heart Rate Responses in Fetuses at Risk for Autism\\
								
%\section {INTERESTS AND SPECIALIZATIONS}
%\begin{tabular}{ l l l }
%Anxiety & \quad \quad Attentional Control & \quad \quad Inhibitory Control\\
%Adolescence & \quad \quad Neurodevelopmental Disorders & \quad \quad Resting State fMRI\\
%Event-Related Potentials & \quad \quad Neuroimaging & \quad \quad Physiology\\ 
%\end{tabular}

\section{AWARDS AND CERTIFICATES}
UC Davis Graduate Student Asssembly Travel Award \hfill 2015-16 Academic Year\\
UC Davis FUTURE Certificate Track \hfill 2015-16 Academic Year\\
UC Davis Graduate Student Asssembly Travel Award \hfill 2014-15 Academic Year\\
ERP Boot Camp (Dr. Steven J. Luck) \hfill Completed July 2014\\
UC Davis Graduate Student Asssembly Travel Award \hfill 2013-14 Academic Year

\section{AFFILIATIONS}
% Society of Biological Society, \textit{Student Member} \hfill 2013-present\\
%Society for Neuroscience, \textit{Student Member} \hfill 2013-present\\
Association for Women in Science, \textit{Student Member} \hfill 2013-present\\
%American Association for the Advancement of Science, \textit{Student Member} \hfill 2013-2014
                
%\section {SCORES \emph{\&} \\ GPA}
%\begin{tabular}{@{}l}                 
%Overall GPA 8 Semesters: 3.67
%\\ Concentration GPA 8 Semesters: 3.70
%\\ Overall GPA Last 4 Semesters: 4.00
%\end{tabular} \hfill
%\begin{tabular}{l@{\hspace*{1em}}}
 %GRE Verbal: 690
%\\ GRE Quantitative: 800
%\\ GRE Writing: 6
%\end{tabular}

\section{DISSERTATION}
\textbf{Behavior and EEG Testing of Teen Anxiety}\\
Mentor: Dr. Tony J. Simon \hfill June 2013 - present\\
A study of 20 adolescents with generalized anxiety disorder and 40 typical controls examining attentional and inhibitory control using event-related potentials, heart rate variability, and behavioral data. Participants complete four tasks and self and parent reports of daily function.


\section{PUBLICATIONS}
%\begin{itemize} \itemsep -2pt
%\item 
{\sl Submitted}: \textbf{Popa AM}, Cruz J, Wong L, Harvey D, Angkustsiri K, Leckliter I, Perez-Edgar K, Simon TJ. Seeing Eye to Eye with Threat: Atypical Threat Bias Responses in Children with 22q11.2 Deletion Syndrome.

{\sl In Progress}: McCabe KL, \textbf{Popa AM}, Durdle C, Amato M, Cabaral M, Wong L, Harvey D, Simon TJ. Quantifying the resolution of spatial and temporal representation in children with 22q11.2 deletion syndrome.

{\sl In Progress}: \textbf{Popa AM}, McCabe KL, Morgan H, Garner J, Harvey D, Amato M,  Simon TJ. Children with 22q11.2 Deletion Syndrome show Visuospatial Impairments on Bisection Tasks.

\section{PRESENTATIONS AND POSTERS} 

\begin{itemize} \itemsep -2pt
\item [] {\sl Selected from 13 Posters (5 first author) and 5 Presentations (4 first author) at International Conferences}\\
\item \textbf{Popa AM}, Mayo D, Durdle C, Morgan H, Shapiro H, Ferrer E, Niendam T, Luck S, Carter C, Simon TJ. Attention and Inhibition Deficits in Youth with 22q11.2DS are Associated with Symptoms of Psychosis Proneness (an IBBC abstract). Poster Accepted at the 17th International Congress of the European Society for Child and Adolescent Psychiatry 2017, Geneva, Switzerland.
\item \textbf{Popa AM}, Durdle C, Morgan H, Shapiro H, Niendam T, Carter C, Luck S, Simon TJ. Highly Psychosis-Prone Adolescents show Increased Capture by Distractor Stimuli and More Effort to Inhibit Emotional Stimuli than Typically Developing Controls. Oral Accepted at the 16th International Congress on Schizophrenia Research 2017, San Diego, CA.
\item \textbf{Popa AM}, Shapiro H, Harvey D, Amato M, Cruz J, Cung N, Reyes D, Simon TJ. Children with 22q11.2 Deletion Syndrome Show Lower Spatial and Temporal Acuity Than TD Children In Continuously Varying Tasks. Abstract Accepted at the 10th Biennial International 22q11.2 Conference 2016, Sirmione, Italy.
%\item Courtney's i22q
%\item Jordan's i22q
%\item Michele's i22q
%\item My Gatlinburg
%\item Courtney's Gatlinburg
%\item Hannah's Gatlinburg
\item \textbf{Popa AM}, Hunsaker N, Deng M, Garner J, Cruz J, Cung N, Reyes D, Simon TJ. Cortical Tissue Volumes Correlate to Cavum Septum Pellucidum Size in Children with 22q11.2 Deletion Syndrome and Typical Controls. Oral Accepted at the 71st Annual Meeting of the Society of Biological Psychiatry 2016, Atlanta, GA.
\item \textbf{Popa AM}, Beaton E, Cruz J, Wong L, Cung N, Harvey D, Simon TJ. Adaptation to a Mild Stressor in Initially Anxious Children was related to their Attention to Perceived Threat in a Dot Probe Experiment. Poster Presented at the 70th Annual Meeting of the Society of Biological Psychiatry 2015, Toronto, ON, Canada.
%\item \textbf{Popa AM}, Angkustsiri K, Brahmbhatt K, Cruz J, Cung N, Harvey D, Leckliter I, Reyes D, Shapiro H, Wong L, Simon TJ. Impact of Cognitive-Affective Interactions on Attentional Control, Inhibition, and Temporal Attention. Oral Presentation Accepted at the 21st International Scientific Meeting of the Velo-Cardio-Facial Syndrome Educational Foundation, Inc 2014, Las Vegas Nevada.
%\item \textbf{Popa AM}, Angkustsiri K, Brahmbhatt K, Cruz J, Cung N, Leckliter I, Quintero A, Reyes D, Shapiro H, Simon TJ. Timecourse of Response to Threat Stimuli in Children with 22q11.2 Deletion Syndrome Informs Understanding of Anxiety. Oral Presentation Accepted at the 9th Annual Meeting of the International 22q11.2 Foundation 2014, Mallorca, Spain.
%\item Angkustsiri K, \textbf{Popa AM}, Simon TJ. Atypical Pupillary Responses To Emotional Faces in Children With Chromosome 22q11.2 Deletion Syndrome. Oral Presentaion Accepted at the Pediatric Academic Societies and Asian Society for Pediatric Research Joint Meeting 2014 Vancouver, BC, Canada.
%\item \textbf{Popa AM}, Angkustsiri K, Brahmbhatt K, Cruz J, Cung N, Leckliter I, Quintero A, Reyes D, Shapiro H, Simon TJ. Atypical Adaptation  Responses to Threat Stimuli in Children with Chromosome 22q11.2 Deletion Syndrome. Poster Presented at the 69th Annual Meeting of the Society of Biological Psychiatry 2014, New York, NY.
%\item Cruz JR, \textbf{Popa AM}, Wong LM, Angkustsiri K, Shapiro H, Fox N, Pine D, Perez-Edgar K, Simon TJ. Examining Attention Bias Towards Threat to Understand Cognition and Anxiety Interactions in 22q11.2DS. Poster presented at the 20th International Scientific Meeting of the Velo-Cardio-Facial Syndrome Educational Foundation 2013, Dublin, Ireland.
%\item Cruz JR, Wong LM, Angkustsiri K, \textbf{Popa AM}, Shapiro HM, Fox N, Pine D, Perez-Edgar K, Simon TJ. Children with Chromosome 22q11.2 Deletion Syndrome Exhibit High Levels of Anxiety and Threat Bias in a Dot Probe Experiment. Poster presented at the 68th Annual Meeting of the Society of Biological Psychiatry 2013, San Francisco, CA.
%\item Sullivan, M. C., Miller, R. J., Winchester, S. B., Barcelos, M., Oliveira, E., \& \textbf{Popa, A}. (2012, May). Developmental Origins Theory and HPA axis function: Evidence from a Longitudinal Study of Preterm Infants at Young Adulthood.  Poster presented at the Massachusetts General Hospital, Yvonne L. Munn Center for Nursing Research, Nursing Research Expo, Boston, MA.
\end{itemize}

%\section{SENIOR HONORS THESIS}


\section{RESEARCH \\ EXPERIENCE}
\textbf{22q11.2 Research Center and Clinic}\\
Dr. Tony J. Simon \hfill MIND Institute at UC Davis, Davis CA\\{\sl Graduate Student Researcher} \hfill June 2013 - present\\ {\sl Rotation Student} \hfill April 2013 - June 2013
\begin{itemize} \itemsep -2pt
\item Analyzed behavioral, eye gaze, and pupilometric data from a dot probe threat bias experiment as they related to self report measures of anxiety and cognition in 47 children with 22q11.2 deletion syndrome and 32 typically developing children
%\item Assistance in generating posters based on these data
%\item End of quarter rotation talk
\item Designed,  tested, collected data, and analyzed four ERP experiments examining adolescents with 22q11.2 deletion syndrome and typical controls on attentional and inhibitory control using neutral and emotional stimuli for a five-year NIH funded grant.
\item Developed tasks for five behavioral experiments on the same study
\item Analyzed resting state fMRI data from over a hundred participants with and without 22q11.2 deletion syndrome to examine differences in three networks isolated using ICA
\item Trained and mentored four junior research assistants and seven volunteer interns

%\item Preparing a manuscript regarding the previous DPTB work
\end{itemize}
\textbf{Reactivation of Neural Ensembles during Very Recent Memory}\\
Dr. Brian J. Wiltgen \hfill Center for Neuroscience at UC Davis, Davis CA\\{\sl Rotation Student} \hfill January 2013 - April 2013
\begin{itemize} \itemsep -2pt
\item Tested 6 mice in a fear learning paradigm 
\item Imaged tissue to determine coactivation of neurons during learning and memory
%\item End of quarter rotation talk presenting protocol and findings
\end{itemize}
\textbf{Poly-I:C Non-human Primate Model of Autism}\\
Dr. Melissa D. Bauman \hfill MIND Institute at UC Davis, Davis CA\\{\sl Rotation Student} \hfill September 2012 - December 2012
\begin{itemize} \itemsep -2pt
%\item Literature search on previous poly-I:C models as performed in rodents
\item Developed tracing protocol and interrater reliability tests for lateral ventricles in macaque subjects' structural MRI scans
%\item Development of interrater reliability tests (and maintenance of reliability) for protocol
\item Traced lateral ventricles in 24 subjects to assess structural abnormalities in primates at risk for autism due to maternal immune activation
%\item Statistical analysis of ventricular volume
%\item End of quarter rotation talk presenting protocol and findings
\end{itemize}
\textbf{Brown Center for the Study of Children at Risk}\\
Dr. Mary C. Sullivan \\ Dr. Stephen J. Sheinkopf \hfill Women and Infants Hospital, Providence RI\\
{\sl Research Assistant} \hfill January 2011 - May 2012 
	\begin{itemize} \itemsep -2pt
	\item \textbf{Preterm Infant to Adult Study:}  A study comparing a longitudinal sample of young adults who had been born pre- or full term  on several measures, including cardiology, executive function and stress response.
	%\item Recruiting, scheduling and consenting participants
	%\item Running one of the participant's three visits, which involves administering an executive function task, a standard social stress test, and collecting saliva samples
	%\item Scoring an executive function task
	%\item Set up a system for digitizing VHS tapes
	%\item Data analysis of the heart rate measures taken during the social stress test, including developing formulae for eliminating outliers, basic summary statistics, and t-tests
	%\item Literature searches for grant building information\\
	\item \textbf{Autism Cry Study:}  A study comparing cries from infants at high or low risk for autism to develop an early predictor of the disorder
	%\item Coded pitch and voicing for infant cry from spectrogram and oscilloscope output
	%\item Wrote a program to create compiled data from analysis software
	%\item Created a system for standardized digitization of about 200 audio cassettes 
	%\item Trained a volunteer in digitization
	%\item Edited audio files for clipping and audio quality
	%\item Working on analysis of the cry files in SPSS for a signature (markers in pitch, energy etc.) for autism risk and similarly for prenatal drug exposure
	%\item Literature searches for question building information
	\end{itemize}
	
	\textbf{Concordance of Movement and Heart Rate Responses in Fetuses at Risk for Autism}\\
Dr. Stephen J. Sheinkopf \hfill Brown University, Providence RI \\
{\sl Senior Honors Thesis Project} \hfill September 2009-December 2010
\begin{itemize}\itemsep-2pt
%\item Honors thesis for the completion of requirements associated with departmental honors
\item Developed a research question and methodology; collected, analyzed and reported on data
\item Compared a sample of fetuses at high risk for autism (one or more confirmed siblings or parents with autism) to a group of normal controls on concordance between movements and heart rate.  This was observed at rest and in response to social and asocial stimuli
%\item Coded actocardiograph strips for different heart rate and movement patterns
%\item Analyzed data using a chi-squared analysis in SPSS
%\item Prepared a paper reporting the results
%\item Defended the thesis in an open format including a presentation and questions, which the general public was invited to
 \end{itemize}

\textbf{Virtual Environment Navigation Laboratory (VENlab)}\\
Dr. William H. Warren \hfill Brown University, Providence RI\\
	{\sl Research Assistant} \hfill May 2007-December 2010
	\begin{itemize} \itemsep -2pt
	\item Ran 6 experimental paradigms in virtual reality and the real world on human participants to study navigation and locomotion
	%\item Obtained informed consent from participants
	%\item Set up the equipment, including a head mounted display, for the virtual reality experiments
	%\item Ran the programmed experiments in a unix based shell and from a Windows environment
	%\item Explained experimental tasks to participants
	%\item Followed participants in virtual reality to ensure participant safety
\end{itemize}


\textbf{Functional Magnetic Resonance Imaging in Theory and Practice}\\
Dr. David Badre \hfill Brown University, Providence RI\\
{\sl Class Research} \hfill September 2009-December 2009
\begin{itemize}\itemsep -2pt
\item Designed, executed, analyzed, and reported an fMRI experiment in small groups.  Our experimental stimuli were comprised of neutral words, words expressing fear, neutral faces, and faces expressing fear to measures brain activation in response to different modalities of fear stimuli
%\item Planned the experiment within the small group.
%\item Selected stimuli by gathering ratings from fellow students.
%\item Standardized stimuli, including size, location on screen and making them monochrome
%\item Programmed stimuli presentation in a block design using E-Prime.  Stimuli presentation order was counterbalanced across subjects, also using E-Prime
%\item Were trained to and performed safety checks for participants (fellow classmates).
%\item Analyzed the data using the SPM package and MATlab
%\item Reported data in a research paper and powerpoint presentation to the class
%We programed the stimuli using E-Prime and analyzed the data using the SPM package and %MATlab.
\end{itemize}

\section{CLINICAL \\ EXPERIENCE} \textbf{The Groden Center}\\
Providence, RI\\
{\sl Treatment Teacher} \hfill June 2009-December 2009 
               
                 \begin{itemize}  \itemsep -2pt % reduce space between items
                 \item Worked as a treatment teacher in a classroom for adolescents with severe autism and profound behavioral problems doing individualized lessons and therapies
                \item   Helped take children and adolescents with severe autism on community field trips                 \end{itemize}
 \textbf{Writers' Group}\\
   The Swearer Center at Brown University, Providence, RI\\
                {\sl Facilitator} \hfill            February 2009-May 2009 
              
                 \begin{itemize}  \itemsep -2pt %reduce space between items
                 \item Planned and facilitiated weekly lessons and activities with a student organized group that prepares writing workshops for adults with developmental disabilites in the local community.
                 %\item Planned weekly lessons and activities
                 %\item With two other students, co-facilitated a group of ten adults, explaining the activities and helping them write and share their work
                 \end{itemize} 
                 
                       \textbf{Bonn Nontapum }\\
                 Cross Cultural Solutions, Bangkok, Thailand\\
                {\sl Volunteer} \hfill        September 2008- December 2008
                
                  \begin{itemize}
									\item Performed play and life skill activities with children at a home for children with special needs in Thailand
                   %\item Took a semester off from school to volunteer at a home for special needs children in Thailand.
                   %\item Played games and helped with lunchtime in a ward for children with cerebral palsy
                   %\item Helped with crafts, sing-a-longs and other activities in a ward for children with autism
                   %\item Helped run free``playtime" for children with non-specific developmental disabilities
                   \end{itemize} 
 
 \section{TEACHING\\EXPERIENCE} 
 \textbf{Neurobiology}\\
 Dr. Lee M. Miller \hfill UC Davis Department of Neurobiology, Physiology, and Behavior, Davis CA\\
 {\sl Teaching Assistant} \hfill April 2015-June 2015
 \begin{itemize}\itemsep -2pt
 \item Planned nine weeks of discussion sections with two co-TAs. Prepared material for an hour of homework review, practice problems, and discussion of lecture material and readings.
 \item Independently led 3 one hour discussion sections for a total of 75 students each week.
 \item Held weekly office hours attended by around six students each session.
 \item Answered numerous e-mails and arranged individual meetings for students who needed extra help.
 \item Developed one homework assignment.
 \item Graded two short answer midterms and one short answer final exam for 200 students with one co-TA.
 \end{itemize}
 
 \textbf{Laboratory on Genes and Behavior}\\
 Dr. Rebecca D. Burwell \hfill Brown University Department of Psychology, Providence RI\\
 {\sl Teaching Assistant} \hfill January 2010-May 2010
\begin{itemize}\itemsep -2pt
\item Set up equipment for behavioral experiments run on knockout mice, including the Morris Water Maze, tail suspension and basic habituation tasks
\item Explained procedures to students and helped them run the tasks
%\item Cleaned up after the lab
\end{itemize}
 

                   
 \section{LEADERSHIP AND\\ COMMUNITY EXPERIENCE}
\textbf{Intertational Rescue Committee}\\
Sacramento, CA\\
{\sl Refugee Empowerment Volunteer} \hfill January 2017 - Present

\textbf{Davis Incubator Group}\\
Davis, CA\\
{\sl President} \hfill September 2016 - Present\\
{\sl Member} \hfill January - August 2016

\textbf{Women in Science and Engineering}\\
Davis, CA\\
{\sl Mentor} \hfill September 2015 - Present

\textbf{Explorations, UC Davis Undergraduate Research Journal}\\Davis, CA\\{\sl Editor} \hfill February 2015 - August 2015\\
{\sl Managing Editor, Physical and Life Sciences} \hfill September 2015 - Present
%\begin{itemize}\itemsep -2pt
%\item Communicate faculty reviewer comments to student authors
%\item Assess reviewed and edited papers for acceptance in a yearly UC Davis publication
%\item Copy-edit student articles
%\item Format articles for publication
%\end{itemize}

\textbf{Neuroimaging Journal Club}\\Davis, CA\\{\sl Student Co-Facilitator} \hfill September 2013 - Present
%\begin{itemize}
%\item Invite faculty guests, select papers and lead student discussions for the student-run neuroimaging journal club
%\end{itemize}

\textbf{UC - Davis Neuroblog}\\ Online through UC Davis\\{\sl Graduate Student Contributer} \hfill September 2013 - Present
%\begin{itemize}
%\item Plan, write and publish posts about neuroscience, advocacy and related topics to a student run blog.
%\end{itemize}

\textbf{The Graduate Academic Achievement and Advocacy Program}\\Davis, CA\\{\sl Graduate Student Volunteer and Mentor} \hfill September 2013 - June 2015
%\begin{itemize}
%\item Advice and assist students from underrepresented minorities one on one on topics such as graduate school applications and science writing
%\item Plan and run workshops for students from underrepresented minorities on topics such as graduate school applications, research assistantships and gap years
%\item Mentor a student
%\end{itemize}

\textbf{Graduate Student Assembly}\\Davis, CA\\{\sl Departmental Representative} \hfill September 2013 - June 2015
%\begin{itemize}
%\item Attend meetings and vote on policy affecting graduate students at UC Davis and in the wider UC graduate student assembly
%\item Publicize information to graduate group
%\end{itemize}
 
 \textbf{Brain Awareness Week}\\ Davis, CA\\{\sl Graduate Student Presenter} \hfill March 2013 - Present
%\begin{itemize}
%\item Developed and presented a new station on Vestibular Nystagmus for a school for struggling high schoolers in Sacramento
%\item Presented posters at a booth at the Farmer's Market
%\item Taught neuroanatomy using sheep brains to high schoolers in Davis
%\end{itemize}
 
 %\textbf{Brown University Dining Services}\\
 %Providence, RI\\
 %{\sl Student Supervisor} \hfill January 2007 - December 2010
 %\begin{itemize}
 %\item Introduced new student workers to the Sharpe Refectory's (Brown University's largest dining hall) kitchen
 %\item Taught students proper technique for preparing ingredients, such and chopping vegetables, hard boiling and peeling eggs, and thawing frozen ingredients
 %\item Ensured ingredients were prepared in time for the chefs who needed them
 %\item Coordinated with professional dining services workers regarding tasks
 %\item Ensured students followed dining services protocols, such as dress code
 %\end{itemize}
 %\textbf{Technology House}\\
 %Residential Program House, Brown University, Providence RI\\
 %{\sl President} \hfill September 2009 - May 2010\\
 %\begin{itemize}
 %\item Ran weekly house meetings in which approximately 40 members were informed of house business and were allowed to discuss house policy
 %\item Ran weekly officer meetings composed of six officers in which we discussed what needed to be done that week for the house
 %\item Made sure officers did what they needed to do for the house to run smoothly
 %\item Started biweekly tech times, in which members held one hour sessions to teach each other technical skills such as soldering
 %\item Codified rules for new members joining the house
 %\end{itemize}
 % {\sl House Manager} \hfill January 2009-May 2009\\
  %\begin{itemize}
  %\item Designed and instituted a new system of house cleaning, in which each week three members were assigned to each of the houses common rooms
  %\item Organized weekly cleanings and ensured members attended their cleanings
  %\item Negotiated with the Office of Residential Life for room allocation for the following year
  %\item Worked with Facilities Management when things needed to be fixed or improved in the physical house
  %\end{itemize}
 %  {\sl Social Chair} \hfill September 2007 - May 2008\\
   %\begin{itemize}
%\item Managed and coordinated Tech House's annual Halloween party, which is attended by approximately 150 Brown Students and features live bands and baked goods
%\item Instituted and coordinated weekly social events such as tea, board games, and barbecues.
%\end{itemize}
%   {\sl Co-facilitator} \hfill September 2009 - May 2010\\
  %Bisexuals Talk and Eat, an LGBTQ support group on campus
  
 % \section{COMPUTER\\SKILLS} Windows, MacOS, Linux, Microsoft Office Suite, Internet, SPSS, E-Prime, SPM, MATLAB, Scheme, OCaml, Java,  \LaTeX\, R, DataGraph, FileMaker, Python, SQL

 

\end{resume}

\end{document}







